External Patch Group Prior Guided Internal Orthogonal Dictionary Learning for Real Image Denoising

### 2016-10-24 CVPR2017_Review_Unified.tex
addd

\subsection{Internal v.s. External Dictionary Learning}
There are two categories of dictionary learning methods in image denoising. One category of methods \cite{epll,pgpd} learns dictionary from external clean images to reconstruct the given noisy images, while the other category of methods \cite{ple,ncsr} directly learns adaptive dictionary from the given noisy image to recover the latent clean image. The two categories of methods are very successful in removing Gaussian noise. However, the noise in real images is generated mostly from the camera sensors, which is highly complex and signal dependent \cite{crosschannel2016}. Besides, the noise in real images has fixed patterns from several main sources \cite{healey1994radiometric}. Therefore, we can hardly seperate the complex noise from the signals without the help of external (correct) information of natural clean images. In this paper, our goal is to employ the external patch group prior to guide the internal noisy PGs to be clustered into correct subspace, and the learning process of internal orthogonal dictionary.

\subsection{Real Image Denoising}
In the last decade, there are many methods \cite{fullyblind,rabie2005robust,Liu2008,almapg,noiseclinic,Zhu_2016_CVPR,crosschannel2016} proposed for real image denoising problem. In the seminar work of BLS-GSM \cite{blsgsm} for real image denoising, Portilla et al. proposed to use scale mixture of Gaussian in overcomplete oriented pyramids to estimate the latent clean images. In \cite{fullyblind}, Portilla proposed to use a correlated Gaussian model for noise estimation of each wavelet subband. The work of Rabie \cite{rabie2005robust} modeled the noisy pixels as outliers which are removed via Lorentzian robust estimator \cite{huber2011robust}. Liu et al. \cite{Liu2008} proposed to use 'noise level function' (NLF) to estimate the noise and then use Gaussian conditional random field to obtain the latent clean image. Gong et al. \cite{almapg} models the noise by mixed $\ell_{1}$ and $\ell_{2}$ norms and remove the noise by sparsity prior in the wavelet transform domain. Later, Lebrun el al. proposed a multiscale denoising algorithm called 'Noise Clinic' \cite{noiseclinic}. This method generalizes the NL-Bayes model \cite{nlbayes} to deal with blind noise and achieves state-of-the-art performance. Recently, Zhu et al. proposed a Bayesian model \cite{Zhu_2016_CVPR} which approximates and remove the noise via Low-Rank Mixture of Gaussian (LR-MoG) model. The commercial software Neat Image \cite{neatimage} first estimate the parameters of noise via a large flat area and then filter the noise accordingly.

>>>>

\subsection{Internal v.s. External Dictionary Learning}
Learning dictionaries to represent images has been successfully used in image modeling \cite{ksvd,ksvdtsp,epll,ple,ncsr,pgpd}.There are mainly two categories of DL methods: 1) External DL methods pre-learned dictionary from a set of clean image patches, and the learned dictionaries are used to encode the noisy image patches for denoising \cite{ksvdtsp,epll,pgpd}. 2) Internal DL methods directly learned dictionary from the patches of given noisy image, and the image denoising is simultaneously done with the DL process \cite{ksvd,ple,ncsr}. The external DL methods is not adaptive to the noisy image, while the internal DL methods is adaptive to the degraded images but it ignores the information hidden in clean images. In this paper, our goal is to employ the external dictionary to guide the learning of internal orthogonal dictionary.

\subsection{Real Image Denoising}
In the last decade, there are many methods \cite{fullyblind,rabie2005robust,Liu2008,almapg,noiseclinic,Zhu_2016_CVPR,crosschannel2016} proposed for real image denoising problem. In the seminar work of BLS-GSM \cite{blsgsm} for real image denoising, Portilla et al. proposed to use scale mixture of Gaussian in overcomplete oriented pyramids to estimate the latent clean images. In \cite{fullyblind}, Portilla proposed to use a correlated Gaussian model for noise estimation of each wavelet subband. The work of Rabie \cite{rabie2005robust} modeled the noisy pixels as outliers which are removed via Lorentzian robust estimator \cite{huber2011robust}. Liu et al. \cite{Liu2008} proposed to use 'noise level function' (NLF) to estimate the noise and then use Gaussian conditional random field to obtain the latent clean image. Gong et al. \cite{almapg} models the noise by mixed $\ell_{1}$ and $\ell_{2}$ norms and remove the noise by sparsity prior in the wavelet transform domain. Later, Lebrun el al. proposed a multiscale denoising algorithm called 'Noise Clinic' \cite{noiseclinic}. This method generalizes the NL-Bayes model \cite{nlbayes} to deal with blind noise and achieves state-of-the-art performance. Recently, Zhu et al. proposed a Bayesian model \cite{Zhu_2016_CVPR} which approximates and remove the noise via Low-Rank Mixture of Gaussians (LR-MoG). The commercial software Neat Image \cite{neatimage} first estimates the parameters of noise via a large flat area and then filters the noise accordingly.
